Followers Are Not Enough: Beyond Structural Communities in Online Social Networks

### 2014-05-06 paper-for_arxiv/results.tex
Added figure with densities by edge type.
This is to replace the distribution by edge type figure.
Added proportion of each edge type by community.

@@

>>>>

\begin{table}
	\caption{The percentage of intra-, inter-, and multi-edges associated with the coverings for each of the four community types.}
	\centering
	\begin{tabular}{l | r r r}
		Community Type & Intra & Inter & Multi \\
		\hline
		Structural & 7.5 & 87.0 &  5.5 \\
		Activity-based & 10.7 & 81.9 & 7.4 \\
		Topic-based & 7.3 & 89.0  & 3.7 \\
		Interaction-based & 42.3 & 47.9 & 9.8
	\end{tabular}
\end{table}

@@

\begin{figure}[!h]
	\centering
	\includegraphics[width=1\textwidth]{densities-edges.eps}
	\caption{The density of edge weights for different community types (rows) and weight types (columns). The red,  blue, and magenta values below each collection of densities indicate the median of weight on intra-, inter-, and multi-edges, respectively.}
	\label{Fig-distributions_by_types}
\end{figure}
